Preprocessing of raw data

### 2018-04-04 02_scripts/01_hyperspectral_indices/05_narrow-band-indices.Rmd
shiny app 2 by 2

---
title: "Calculate all possible narrow band indices"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

# Information about this script

This script accounts for either local (laptop) or server (MCCOY) runs. Path is adjusted using object `prefix`

Since this is an `.Rmd` file it cannot simply be called using `source()` or `Rscript` (server).

Instead, please use the [custom function `runAllChunks()`](http://stackoverflow.com/a/24754637/4185785) inside an R console with the `.Rmd` file as input. 
It is recommended to put this function into your .Rprofile to have it available whenever you start an R session.

**Attention**

@@

```{r}
pacman::p_load(raster, hsdar, pbapply, parallel, tidyverse, here, magrittr)
```

# Load wavelength and rasters

```{r}
wavelength <- readRDS("/home/shares/data/LIFE/mod/hyperspectral/wavelength.Rds")

list.files("/home/shares/data/LIFE/mod/hyperspectral/atm-cropped", 
           pattern = ".tif$", full.names = TRUE) %>%
  lapply(function(x) brick(x)) %>% 
  lapply(function(x) HyperSpecRaster(x, wavelength)) -> hyperspecs
```

# account for use on local laptop or server
```{r}
if (detectCores() > 10) {
  cores <- 28
} else (cores <- 1)
```

# do calculation of narrow band indices

@@

```{r}
## Calculate NBI
# hyperspecs <- list(hyperspecs[[1]])

hyperspecs %>% 
  pblapply(function(x) 
    nbi_raster(x, filename = gsub(".tif", ".grd", 
                                  "/home/shares/data/LIFE/mod/hyperspectral/narrow-band-indices/",
                                         "narrow-band-indices-", basename(x@file@name))), cl = cores) 
```

>>>>

---
title: "Calculate all possible narrow band indices"
output: 
  bookdown::html_document2:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      cache = TRUE)
```

@@

```{r, results='hide'}
library(raster)
devtools::install_github("pat-s/hsdar")
library(hsdar)
library(pbmcapply)
library(glue)
library(magrittr)
library(purrr)
```

# Specify wavelength

```{r}
wavelength = readRDS("/data/patrick/mod/hyperspectral/wavelength.Rds")
```

# Read rasters (cropped by plot)

## list files

```{r}
list.files("/data/patrick/mod/hyperspectral/atm-cropped", 
                    pattern = ".tif$", full.names = TRUE) %>% 
  map(~ brick(.x)) -> spectral_data
```

# Coerce to class "HyperSpecRaster"

```{r}
hyperspecs = map(spectral_data, function(x) HyperSpecRaster(x, wavelength))
```

# Create narrow band indices

@@

```{r, cache=FALSE}
tmp <- pbmclapply(hyperspecs, function(x)  
  nbi_raster(x,
             filename = str_replace(glue("/data/patrick/mod/hyperspectral/",
                             "narrow-band-indices/narrow-band-indices-{name}",
                             name = basename(x@file@name)), ".tif", ".grd"), mc.cores = 15)) 
rm(tmp)
```

```{r}
sessionInfo()
```

### 2018-04-04 02_scripts/01_hyperspectral_indices/06_extract-indices-to-points.Rmd
shiny app 2 by 2

---
title: "Extract indices to points"
output: html_notebook
editor_options: 
chunk_output_type: inline
---

# Information about this script

This script accounts for either local (laptop) or server (MCCOY) runs. Path is adjusted using object `prefix`

Since this is an `.Rmd` file it cannot simply be called using `source()` or `Rscript` (server).

Instead, please use the [custom function `runAllChunks()`](http://stackoverflow.com/a/24754637/4185785) inside an R console with the `.Rmd` file as input. 
It is recommended to put this function into your .Rprofile to have it available whenever you start an R session.

```{r}
pacman::p_load(raster, sf, here, magrittr, tidyverse, pbapply, parallel)
```

>>>>

---
title: "Extract indices to points"
output: 
  bookdown::html_document2:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      cache = TRUE)
```

```{r, results='hide'}
library(raster)
devtools::install_github("pat-s/hsdar")
library(hsdar)
library(pbmcapply)
library(glue)
library(magrittr)
library(sf)
library(purrr)
```

### 2018-04-04 02_scripts/02_preprocessing.Rmd
shiny app 2 by 2

```{r}
library(purrr)
library(here)
library(readr)
library(tibble)
library(glue)
library(raster)
```

@@

map(names, 
    ~ as_tibble(read.table(file = glue("/data/patrick/mod/survey_data/2016/{.x}.txt"), 
                           sep = "\t", dec = ",", header = TRUE))) %>% 
  set_names(names) -> data_all
```

@@

```{r}
map(names,
    ~ brick(glue("/data/patrick/mod/hyperspectral/all-veg-indices/all-veg-indices-{.x}.gri"))) %>% 
  set_names(names) -> indices_all
```

@@

>>>>

```{r}
library(purrr)
library(here)
library(readr)
library(tibble)
library(glue)
library(raster)
library(sf)
library(dplyr)
library(tidyr)
library(magrittr)
library(stringr)
```

@@

map(names, 
    ~ as_tibble(read.table(file = glue("/data/patrick/mod/survey_data/2016/{.x}.txt"), 
                           sep = "\t", dec = ",", header = TRUE,
                           stringsAsFactors = FALSE, 
                           na.strings=c("")))) %>% 
  set_names(names) %>% 
  map(~ rename_all(.x, tolower)) -> data_tbl
```

Laukiz2 has no coordinate info in the txt file. We need to read the shapefile and join them.

### Join Laukiz2 coords

```{r}
laukiz2_coords = st_read("/data/patrick/raw/survey_data/2016/laukiz2/arboles/Laukiz2_arboles_ETRS89.shp")

data_tbl$laukiz2 = left_join(data_tbl$laukiz2, laukiz2_coords, 
                             by = c("num.arbol" = "id_arbol"))
```

Drop observations with no coordinate information.

```{r}
data_tbl %<>% 
  map(~ drop_na(.x, c("x", "y")))
```

Coerce to `sf` objects.

```{r}
map(data_tbl, ~ st_as_sf(.x, coords = c("x", "y"))) -> data_sf
```

Select variables related to defoliation.

```{r}
data_sf %<>% 
  map(~ select(.x, contains("def")))
```

Laukiz2 needs some clean up:

"no" -> 0
"*" -> NA
Coerce from chr to int.
Calculate "deftot" which is the mean of all three parts (bottom, mid, top).

`rowSums` will thrown an error due to the "geometry" column so we need to add `drop = TRUE`.

```{r}
data_sf$laukiz2 %<>% 
  mutate(x..de.defoliacion.parte.media = 
           replace(.$x..de.defoliacion.parte.media, 
                   .$x..de.defoliacion.parte.media == "no", "0")) %>% 
  mutate(x..defoliacion.en.punta = 
           replace(.$x..defoliacion.en.punta, 
                   .$x..defoliacion.en.punta == "no", "0")) %>% 
  mutate(x..defoliacion.base = 
           replace(.$x..defoliacion.base,
                   .$x..defoliacion.base == "no", "0")) %>% 
  mutate(x..defoliacion.base = 
           replace(.$x..defoliacion.base,
                   .$x..defoliacion.base == "*", NA)) %>% 
  mutate_if(is.character, as.numeric) %>% 
  mutate(deftot = as.integer(rowMeans(.[, 1:3, drop = TRUE], na.rm = TRUE)))
```

@@

```{r}
map(names,
    ~ brick(glue("/data/patrick/mod/hyperspectral/all-veg-indices/all-veg-indices-{.x}.gri"))) %>% 
  set_names(names) -> veg_indices_all
```

@@

```{r}
map(names,
    ~ brick(glue("/data/patrick/mod/hyperspectral/narrow-band-indices/narrow-band-indices-{.x}.gri"))) %>% 
  set_names(names) -> nbi_indices_all
```
